Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-07-01 paper/Draft.tex
final submission of 2nd paper

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage[a4paper,bindingoffset=0.2in,%
left=1in,right=1in,top=1.2in,bottom=1.2in,%
footskip=.25in]{geometry}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,      
	urlcolor=blue,
	citecolor=blue
}
\usepackage{natbib}

@@

	\begin{abstract}
		Surveys on density forecasts of macroeconomic variable that are not available until recent provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households. Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of analysis.

@@

	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade. This has been also engined by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing these theories empirically.  On one hand, various theories built upon different micro foundations produce somewhat similar macro patterns. For instance, the notion of expectation rigidity micro-founded by different theories mostly generate sluggish response to new information.  On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.

	This paper extends this research effort by bringing an additional moment of forecasts into perspective, i.e. uncertainty. Specifically, in this paper I first derive the testable predictions from various theories on uncertainty and carefully compare the differences mostly obvious seen from uncertainty. Second empirically I test and estimate these implications utilizing the recently available probabilistic forecasts from both professional forecasters survey and household survey. Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models. In the same time, the degree of rigidity appears to be shock-specific and bears the difference to households and professional forecasters.

	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of values of the variable of forecast\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.}. With density forecasts,  variance of individual forecast can be estimated as an indicator of the uncertainty. Across different vintages of the forecast, the revision in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency. Besides, the dispersion of uncertainty across agents, and its relationship with other moments widely looked by the literature, such as forecast errors and disagreements provide many insights as to how the agents expectation actually work.

	This paper is related to three strands of literature. First, recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data. For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}. More recent examples include \citet{coibion2018firms} on firms' managers. In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demographics and macroeconomic history experienced(\citet{malmendier2015learning}, \citet{das2017socioeconomic},etc.). In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}.  However, all of these research simply rely upon point forecasts instead of density forecast or surveyed uncertainty. This is one theme on which this paper differs from the existing literature.

@@

	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probiblistic questions measuring subjective uncertainty in economic surveys. Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people}and other work have all shown that this is actually less of a concern. \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses. Broadly speaking, the advocators have argued that going beyond revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.  This insight holds for not only point forecast, but also and even more importantly, for uncertainty.

	The paper is organized as followed. Section \label{theory} first sets up a common framework in which testable various theories can be compared. Also, I derive the testable predictions from these theories for individual and population uncertainty as well as other moments. Section \ref{empirical} discusses the survey data used for this paper, and presents both the stylized patterns and time series regressions that test the implications of these theories.   Section \ref{ShockBased} includes results from estimating the impulse response of forecast moments to externally identified shocks.  Section \ref{Conclusion} concludes the paper and discusses the plan for the next step.

@@

	An agent $i$ is forming expectations about a stochastic variable $y^i_{t+h}$. The supscript $i$ can be dropped if it is an aggregate (i.e. inflation) variable instead of individual specific  (i.e. household income or house value). This paper focuses on forecasting of aggregate variables, in particular, inflation. So we can simply denote the variable as $y_{t+h}$.  \footnote{Only in the context of aggregate variable, it is justified to study the population moments such as average expectations and disagreements. Studying expectations of idiosyncratic variables requires individual panel data, as well as the idiosyncratic realizations of the variable. }

@@

	$I_{i,t}$ is the information set available for individual $i$ at time t. The information set can be  agent specific, thus it has subscript $i$.  The specific content contained in $I_t$ varies from different models of expectation. For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instantaneously. So the information set may not contain the most recent realization of the variable of forecast $y_t$. \footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$. Examples of such include multi-prior or model uncertainty. \citet{hansen2001robust}, \citet{hansen2008robustness}, etc.}

@@

	The population analogues of individual mean forecast, uncertainty and forecast errors are simply the average of the individual moments taken across agents. Denote them as $\bar y_{t+h|t}$, $\bar \sigma^2_{t+h|t}$, and $\overline{FE}_{t+h|t}$, respectively. Hereafter, they are termed as population mean forecast, population uncertainty and population forecast error, respectively. In addition, disagreements is defined as the cross-sectional variance of mean forecasts of individual agents.  Denote it as $\overline{Var}_{t+h|t}(y_{i,t+h|t}) $. To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.

	In summary, we have 3 individual moments and 4 population moments listed in below in Table \ref{MomSum}.

@@

	Finally, we assume the underlying true process of $y_{t}$ is $AR(1)$ with persistency parameter $0<\rho <1$ and i.i.d. shock $\omega_t$.

@@

	Although we make the assumption of i.i.d. shock here. The framework allows for the possibility of time-varying volatility, i.e. the variance of $\omega_t$ is thus $\sigma^2_{t,\omega}$ with time subsript.

@@

	In the FIRE benchmark,  it is assumed that all agents perfectly observe $y_t$ at time $t$ and understand the true process of $y$. Therefore, individual forecast is $\rho^h y_t $, which is shared by all agents. Therefore, it is also equal to average forecast.

@@

	I use supscrit of $*$ to denote all the moments according to FIRE. It is easy to see that the forecast error is orthogonal to information available till time $t$. This provides the a well known null hypothesis of FIRE.

	The second implication from FIRE here is that forecast errors of non-overlapping horizon are not correlated. (Equation \ref{NoSerialCorrFE}). For instance, forecast error at time $t$ and that at time $t+h$ or further are not serially correlated. This is not the case within $h$ periods as the realized shocks in overlapping periods enter both forecast errors.  These FE-based restrictions of FIRE provide the foudnations for the tests used in Table \ref{NullTest}.

@@

	Concerning uncertainty, the first simple implication by FIRE is that all individual shares the same degree of uncertainty. The uncertainty about future $y$ simply comes from uncertainty about unrealized shocks between $t$ and $t+h$. With the same model in mind (Equation \ref{AR_process})and same information $y_t$, everyone's uncertainty is equal to the weighted sum of the future volatility before its realization. (Equation \ref{VarREIndPop}). In FIRE, there is neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{jurado2015measuring}'s terminology.}

@@

	The time series behavior of h-year-ahead uncertainty, i.e. $\sigma^2_{t+h|t}$, $\sigma^2_{t+h+1|t+1}$, etc, depends on the true process of $y$. Specifically, it depends if $\sigma^2_\omega$ is time varying. If time-invariant, h-period-ahead uncertainty is simply as constant. In baseline case we make such an assumption, in general it may not be true. \footnote{\citet{xx} on time-varying volatility.}

	The testable implication of rationality lies in the revision in uncertainty. Hereafter, we refer revision (instead of change) as the difference of moments across vintages of forecast with the fixed terminate date of realization. For instance, the difference between the uncertainty about $y_{t+h}$ at time $t$ and the uncertainty about $y_{t+h}$ at time $t-1$.

	More generally,  denote the forecast of $y_{t+h}$ over horizon of $h-k$ as $y_{t+h|t+k} \quad \forall k =0,1...h$. Then the uncertainty at different points of the $k$ is the following.

@@

	Moving from $t$ to $t+1$, for instance, revision in uncertainty can be also expressed as a function of previous revision.

@@

	The theory of sticky expectation (\citet{mankiw2002sticky}, \citet{carroll2003macroeconomic} etc.), regardless of various micro-foundations, builds upon the assumption that agents do not update information instantaneously as they do in FIRE. One tractable assumption is that there is a homogenous Poisson rate $\lambda$ of updating among the population. Specifically, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.

@@

	In FIRE, updating at each period $t$ resolves only the uncertainty about the shocks that have just realized in $t$. In constrast, in SE each updating resolves the uncertainty about all the realized shocks since last update. From $t-\tau$ to $t$, the revision in uncertainty is

@@

	FIRE basically assumes  $\tau=1$ for all the agents and all the time, namely all agents' last update takes place in previous period. So setting $\tau =1$ in above equation gives the reduction in uncertainty in FIRE. The reduction in uncertainty is greater in SE for any $\tau>1$ than FIRE.

	In individual level, the key difference between FIRE and SE is that the later does not reduce uncertainty  as efficiently as in the former primarily because of the rigidity incorporating new information. In the same time, note that the rigidity in updating according to SE cannot be systematically observable in the individual level, both in terms of forecasts errors and uncertainty. This is because the behaviors of each individual forecast specifically depends on if the she updates or not in that period.

	Relying upon the law of large numbers, one can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$. \footnote{\citet{carroll2003macroeconomic} is one notable example of this.}

@@

	Similarly, the inefficiency of reducing uncertainty in SE takes the following form in aggregate level. Average uncertainty at any point of time is now a weighted average of uncertainty to agents whose last updates have taken place in different periods of past.

	\begin{eqnarray}\label{VarSEPop}
		\begin{aligned}
			\bar \sigma^2_{t+h|t} & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction who non-updater until }t-\tau} \underbrace{\sigma^2_{t+h|t-\tau}}_{\text{ uncertainty of most recent update at }t-\tau} \\
			& = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
		\end{aligned}
	\end{eqnarray}

	Since not all agents incorporate the recent realized shocks, the revision in average uncertainty exhibits serial correlation described in Equation \ref{VarSERv}. It is a weighted average of the resolution of uncertainty from the most recent shocks and its lagged counterpart.

@@

	In particular, the second component is the information gain from most recent realization of the shock underweighted by $\lambda<1$. The first component is the inefficiency sourced from stickiness of updating. The higher rigidity (lower $\lambda$), the smaller the efficiency gain or uncertainty reduction compared to in FIRE.

@@

	A class of models (\citet{lucas1972expectations}, \citet{sims2003implications}, \cite{woodford2001imperfect} etc.), noisy information(NI) hereafter, describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.  The starting assumption is that agent cannot observe the true variable perfectly. Unlike SE, it is assumed that agents keep track of the realizations of signals instantaneously all the time.

@@

	What is different from FIRE is that the agent makes her best guess of $y_t$ using Kalman filtering at time $t$. Specifically, mean forecast of individual $i$ is the posterior mean based on her prior and realized signals $s_{i,t}$.

@@

	The under-reaction to news generate serial correlation of forecast errors with the coefficient being $\rho^2(1-PH)$. it does not only depend on $PH$, but also the forecast horizon $h$. As $\rho<1$, the rigidity declines with longer horizon. In this regard, the rigidity implied by NI and SE are different because the form is fixed and the later is horizon dependent.

	What differentiates average forecast from individual's is the role played by private signals. On average, private signals cancel out across agents, therefore, only public signals enter in average forecast, thus, average forecast errors (Equation \ref{FENIPop}).

@@

	Kalman filtering also updates the variance according to rule normal updating.   The posterior variance at time $t$ is a linear function of uncertainty in previous period and variance of signals.

@@

	This directly gives the revision in uncertainty from time $t-1$ to $t$. The newly arrived information, although noisy, still brings about information gains, thus leading to an unambiguously drop on uncertainty. But due to the signal is not perfect, i.e. $\Sigma^v \neq 0$, there is inefficiency in reducing uncertainty compared to FIRE. This mea

@@

	As a result, the revision in h-period-ahead uncertainty from $t-1$ to $t$ only partially reacts to the resolution of  uncertainty from newly realized shock $\omega_t$ in the passed period.

@@

	Figure \ref{IllustrateNI} illustrates the Kalman filtering problem over the $10$ period horizon from to $t$ to $t+10$  following one-time shock of one standard deviation $\omega_t$.  For illustration purpose, I assume that both private and public signals have the equal degree of noisiness and their standard deviation is equal to the unconditional standard deviation of $y$, i.e. $\sqrt{\frac{\sigma^2_\omega}{1-\rho^2}}$.  A particular draw of public and private signals from their respective conditional distributions given $y_t$ are plotted.

@@

	The sharp rise in nowcasting uncertainty in the beginning of the period is only humbly reflected in the forecasting uncertainty seems counterintuitive in the first sight. Actually this is due to nowcasting uncertainty is discounted by the factor of $\rho^2(h-k)$.  (Equation \ref{VarNIEq}). It is also interesting that for the particular configurations of noisiness of the signals, the drop in forecasting uncertainty from NI is not as inefficient as one may have expected compared to FIRE.  This has important quantitative implications for NI models. In particular, the nosiness of the signals need to be consistent with the degree of rigidity. I will return this point in the next section.

	\begin{figure}[ht]
		\centering
		\includegraphics[width=13cm]{figures/ni_illustration.png}  
		\caption{Nowcasting and Forecasting in Noisy Information}
		\label{IllustrateNI}
	\end{figure}

	NI also predicts non-zero disagreements in the presence of private signals. The behavior of disagreements across agents come from the difference in realized private signals. Specifically, it is equal to the following.

@@

	The implications for disagreements are straightforward. First, the disagreements decreases with the forecast horizon for the reason of discounting. Second, the disagreements depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$. Third, similar to SE, the disagreements also increase with the rigidity parameter $P$ in this model.

@@

	Taking stock, both SE and NI predict rigidity in expectation incorporating arrival of new information. In the former context, the rigidity comes from the simple non-updating of the most realization of the variable. In the later case, the rigidity comes from a partial reaction to new information due to its nosiness.  In addition to forecast and disagreements, the rigidity is also reflected in the dynamics of uncertainty.  Uncertainty in SE does not resolve as rapid as in FIRE because the newly realized shocks do not get updated by some of the agents. While in NI, the drop in uncertainty is dampened because the there is positive uncertainty associated with the real-time realization of the variable.

	Figure \ref{ir_pop} illustrates the impulse response of population moments to a hypothetical one-time shock of size one unit at time $t$ according to different theories. Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to the one unconditional standard deviation of $y$.  And the $\lambda$ is set to be $0.25$, implying on average an update interval of four quarters.

	Both FE and disagreements from SE and NI exhibit sluggish adjustment following the shock as we have anticipated. Both pick up in the time of the shock and gradually declines over the horizon as the forecaster approaches terminate date $t+10$. The difference is that in NI, both the forecast and forecast errors move up and downs around the the smooth version of the SE since noise is not perfect.

	The dynamic of disagreements and uncertainty, however,  illustrate one parametric differences between SE and NI. In particular,  the initial pick in disagreements is higher for NI compared to SE for the particular parameter values. This implies that the noise of the private signal that drives the disagreements in NI exceeds that the extent to which the agents do not simultaneously update in SE. \footnote{Another subtle point is that if the disagreements jump the highest in the time of the shock turns out depend on value of $\lambda$. In the fixed horizon forecasting, $\lambda=0.5$ is the maximizer of disagreements.}

>>>>

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage[a4paper,bindingoffset=0.2in,%
left=1in,right=1in,top=1.2in,bottom=1.2in,%
footskip=.25in]{geometry}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,      
	urlcolor=blue,
	citecolor=blue
}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{threeparttable}

@@

	\begin{abstract}
		Surveys on density forecasts of macroeconomic variable that are not available until recent provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation as well as other stylized facts across economists and households.  Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of the analysis.

@@

	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade. This has been also engined by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing these theories empirically.  On one hand, various theories built upon different micro foundations produce somewhat similar macro patterns. For instance, the notion of expectation rigidity micro-founded by different theories mostly generate a sluggish response to new information.  On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.

	This paper extends this research effort by bringing an additional moment of forecasts into perspective, i.e. uncertainty. Specifically, in this paper, I first derive the testable predictions from various theories on uncertainty and carefully compare the differences mostly obvious seen from uncertainty. Second empirically I test and estimate these implications utilizing the recently available probabilistic forecasts from both professional forecasters survey and household survey. Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models. In the same time, the degree of rigidity appears to be shock-specific and bears the difference to households and professional forecasters.

	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of values of the variable of forecast\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.}. With density forecasts,  the variance of individual forecast can be estimated as an indicator of the uncertainty. Across different vintages of the forecast, the revision in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency. Besides, the dispersion of uncertainty across agents, and its relationship with other moments widely looked by the literature, such as forecast errors and disagreements provide many insights as to how the agents expectation actually work.

	This paper is related to three strands of literature. First, the recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data. For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}. More recent examples include \citet{coibion2018firms} on firms' managers. In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demographics and macroeconomic history experienced(\citet{malmendier2015learning}, \citet{das2017socioeconomic},etc.). In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}.  However, all of these research simply rely upon point forecasts instead of density forecast or surveyed uncertainty. This is one theme on which this paper differs from the existing literature.

@@

	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probabilistic questions measuring subjective uncertainty in economic surveys. Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have all shown that this is actually less of a concern. \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses. Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.  This insight holds for not only point forecast, but also and even more importantly, for uncertainty.

	The paper is organized as followed. Section \label{theory} first sets up a common framework in which testable various theories can be compared. Also, I derive the testable predictions from these theories for individual and population uncertainty as well as other moments. Section \ref{empirical} discusses the survey data used for this paper and presents both the stylized patterns and time series regressions that test the implications of these theories.   Section \ref{ShockBased} includes results from estimating the impulse response of forecast moments to externally identified shocks.  Section \ref{Conclusion} concludes the paper and discusses the plan for the next step.

@@

	An agent $i$ is forming expectations about a stochastic variable $y^i_{t+h}$. The superscript $i$ can be dropped if it is an aggregate (i.e. inflation) variable instead of individual-specific  (i.e. household income or house value). This paper focuses on forecasting of aggregate variables, in particular, inflation. So we can simply denote the variable as $y_{t+h}$.  \footnote{Only in the context of aggregate variable, it make sense to study the population moments such as average expectations and disagreements. Studying expectations of idiosyncratic variables requires individual panel data, as well as the idiosyncratic realizations of the variable. }

@@

	$I_{i,t}$ is the information set available for individual $i$ at time t. The information set can be  agent specific, thus it has subscript $i$.  The specific content contained in $I_t$ varies from different models of expectation. For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instantaneously. So the information set may not contain the most recent realization of the variable of forecast $y_t$. \footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$. For instance, \citet{patton2010forecasters} finds that the disagreements are driven by not only difference in information but also heterogeneity in prior and models. More theoretical work includes multi-prior or model uncertainty such as \citet{hansen2001robust}, \citet{hansen2008robustness}, etc.}

@@

	The population analogs of individual mean forecast, uncertainty and forecast errors are simply the average of the individual moments taken across agents. Denote them as $\bar y_{t+h|t}$, $\bar \sigma^2_{t+h|t}$, and $\overline{FE}_{t+h|t}$, respectively. Hereafter, they are termed as the population mean forecast, population uncertainty and population forecast error, respectively. In addition, disagreement is defined as the cross-sectional variance of mean forecasts of individual agents.  Denote it as $\overline{Var}_{t+h|t}(y_{i,t+h|t}) $. To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.

	To abuse the language, I refer to the 3 individual indicators and 4 population indicators as moments and they are  listed in Table \ref{MomSum}

@@

	Finally, we assume the underlying true process of $y_{t}$ is $AR(1)$ with persistence parameter $0<\rho <1$ and i.i.d. shock $\omega_t$.

@@

	Although we make the assumption of i.i.d. shock, the framework allows for the possibility of time-varying volatility, i.e. the variance of $\omega_t$ is thus $\sigma^2_{t,\omega}$ with time subscript.

@@

	In the FIRE benchmark,  it is assumed that all agents perfectly observe $y_t$ at time $t$ and understand the true process of $y$. Therefore, the individual forecast is $\rho^h y_t $, which is shared by all agents. Therefore, it is also equal to the average forecast.

@@

	I use superscript of $*$ to denote all the moments according to FIRE. It is easy to see that the forecast error is orthogonal to information available till time $t$. This provides the a well known null hypothesis of FIRE.

	The second implication from FIRE here is that forecast errors of non-overlapping horizon are not correlated. (Equation \ref{NoSerialCorrFE}). For instance, forecast error at time $t$ and that at time $t+h$ or further are not serially correlated. This is not the case within $h$ periods as the realized shocks in overlapping periods enter both forecast errors.  These FE-based restrictions of FIRE provide the foundations for the tests used in Table \ref{NullTest}.

@@

	Concerning uncertainty, the first simple implication by FIRE is that all individual shares the same degree of uncertainty. The uncertainty about future $y$ simply comes from uncertainty about unrealized shocks between $t$ and $t+h$. With the same model in mind (Equation \ref{AR_process}) and the same information $y_t$, everyone's uncertainty is equal to the weighted sum of the future volatility before its realization. (Equation \ref{VarREIndPop}). In FIRE, there are neither disagreements about mean, nor disagreements about the uncertainty \footnote{This is the same to \citet{jurado2015measuring}'s terminology.}

@@

	The time series behavior of h-year-ahead uncertainty, i.e. $\sigma^2_{t+h|t}$, $\sigma^2_{t+h+1|t+1}$, etc, depends on the true process of $y$. Specifically, it depends if $\sigma^2_\omega$ is time-varying. If time-invariant, h-period-ahead uncertainty is simply as constant. In baseline case, I make such an assumption, in general it may not be true. \footnote{For example, \citet{justiniano2008time}, \citet{vavra2013inflation} on time-varying volatility of inflation.}

	The testable implication of rationality lies in the revision of uncertainty. Hereafter, we refer revision (instead of change) as the difference of moments across vintages of forecast with the fixed terminate date of realization. For instance, the difference between the uncertainty about $y_{t+h}$ at time $t$ and the uncertainty about $y_{t+h}$ at time $t-1$.

	More generally,  denote the forecast of $y_{t+h}$ over the horizon of $h-k$ as $y_{t+h|t+k} \quad \forall k =0,1...h$. Then the uncertainty at different points of the $k$ is the following.

@@

	Moving from $t$ to $t+1$, for instance, revision in uncertainty can be also expressed as a function of the previous revision.

@@

	The theory of sticky expectation (\citet{mankiw2002sticky}, \citet{carroll2003macroeconomic} etc.), regardless of various micro-foundations, builds upon the assumption that agents do not update information instantaneously as they do in FIRE. One tractable assumption is that there is a homogenous Poisson rate $\lambda$ of updating among the population. Specifically, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with the probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since the last update.

@@

	In FIRE, updating at each period $t$ resolves only the uncertainty about the shocks that have just realized in $t$. In contrast, in SE each updating resolves the uncertainty about all the realized shocks since the last update. From $t-\tau$ to $t$, the revision in uncertainty is

@@

	FIRE basically assumes  $\tau=1$ for all the agents and all the time, namely all agents' last update takes place in the previous period. So setting $\tau =1$ in the above equation gives the reduction in uncertainty in FIRE. The reduction in uncertainty is greater in SE for any $\tau>1$ than FIRE.

	In the individual level, the key difference between FIRE and SE is that the later does not reduce uncertainty  as efficiently as in the former primarily because of the rigidity incorporating new information. In the same time, note that the rigidity in updating according to SE cannot be systematically observable in the individual level, both in terms of forecasts errors and uncertainty. This is because the behaviors of each individual forecast specifically depend on if she updates or not in that period.

	Relying upon the law of large numbers, one can derive testable predictions about population moments that allow us perform tests of sticky expectation and recover rigidity parameter $\lambda$. \footnote{\citet{carroll2003macroeconomic} is good example of this for households.}

@@

	Similarly, the inefficiency of reducing uncertainty in SE takes the following form in the aggregate level. Average uncertainty at any point of time is now a weighted average of uncertainty to agents whose last updates have taken place in different periods of past.

	\begin{eqnarray}\label{VarSEPop}
		\begin{aligned}
			\bar \sigma^2_{t+h|t} & = \sum^{+\infty}_{\tau =0} \underbrace{\lambda (1-\lambda)^\tau}_{\text{fraction of non-updater until }t-\tau} \underbrace{\sigma^2_{t+h|t-\tau}}_{\text{ uncertainty of most recent update at }t-\tau} \\
			& = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \sum^{h+\tau}_{s=0}\rho^{2s} \sigma^2_{\omega}
		\end{aligned}
	\end{eqnarray}

	Since not all agents incorporate the recently realized shocks, the revision in average uncertainty exhibits serial correlation described in Equation \ref{VarSERv}. It is a weighted average of the resolution of uncertainty from the most recent shocks and its lagged counterpart.

@@

	In particular, the second component is the information gain from the most recent realization of the shock underweighted by $\lambda<1$. The first component is the inefficiency sourced from the stickiness of updating. The higher rigidity (lower $\lambda$), the smaller the efficiency gain or uncertainty reduction compared to in FIRE.

@@

	A class of models (\citet{lucas1972expectations}, \citet{sims2003implications}, \cite{woodford2001imperfect}, etc.), noisy information(NI) hereafter, describes the expectation formation as a process of extracting or filtering true variable $y_t$ from a sequence of realized signals.  The starting assumption is that the agent cannot observe the true variable perfectly. Unlike SE, it is assumed that agents keep track of the realizations of signals instantaneously all the time.

@@

	What is different from FIRE is that the agent makes her best guess of $y_t$ using Kalman filtering at time $t$. Specifically, the mean forecast of individual $i$ is the posterior mean based on her prior and realized signals $s_{i,t}$.

@@

	The under-reaction to news generate serial correlation of forecast errors with the coefficient being $\rho^2(1-PH)$. it does not only depend on $PH$, but also the forecast horizon $h$. As $\rho<1$, the rigidity declines with a longer horizon. In this regard, the rigidities implied by NI and SE are different because the form is fixed and the later is horizon dependent.

	What differentiates average forecast from individual's is the role played by private signals. On average, private signals cancel out across agents, therefore, only public signals enter the average forecast, thus, average forecast errors (Equation \ref{FENIPop}).

@@

	Kalman filtering also updates the variance according to the rule of normal updating.   The posterior variance at time $t$ is a linear function of uncertainty in the previous period and variance of signals.

@@

	This directly gives the revision in uncertainty from time $t-1$ to $t$. The newly arrived information, although noisy, still brings about information gains, thus leading to an unambiguously drop on uncertainty. But due to the signal is not perfect, i.e. $\Sigma^v \neq 0$, there is inefficiency in reducing uncertainty compared to FIRE.

@@

	As a result, the revision in h-period-ahead uncertainty from $t-1$ to $t$ only partially reacts to the resolution of  uncertainty from newly realized shock $\omega_t$ in the past period.

@@

	Figure \ref{IllustrateNI} illustrates the Kalman filtering problem over the $10$-period horizon from to $t$ to $t+10$  following a one-time shock of one standard deviation of $\omega_t$.  For illustration purpose, I assume that both private and public signals have an equal degree of noisiness and their standard deviation is equal to the unconditional standard deviation of $y$, i.e. $\sqrt{\frac{\sigma^2_\omega}{1-\rho^2}}$.  A particular draw of public and private signals from their respective conditional distributions given $y_t$ are plotted.

@@

	In the first sight, the sharp rise in nowcasting uncertainty at the beginning of the period being only humbly reflected in the forecasting uncertainty seems counterintuitive. Actually this is due to nowcasting uncertainty is discounted by the factor of $\rho^2(h-k)$.  (Equation \ref{VarNIEq}). It is also interesting that for the particular configurations of the noisiness of the signals, the drop in forecasting uncertainty from NI is not as inefficient as one may have expected compared to FIRE.  This has important quantitative implications for NI models. In particular, the nosiness of the signals needs to be consistent with the degree of rigidity. I will return this point in the next section.

	\begin{figure}[ht]
		\centering
		\includegraphics[width=13cm]{figures/ni_illustration.png}  \\
		{\footnotesize Note: the top two figures plot the nowcasting of $y_{t+k}$  at time $t+k$ and forecasting of $y_{t+h}$ at time $t+k$  based on a Kalman filtering together with FIRE after a one-time shock of one unit at time $t$. The nowcasting and forecasting uncertainty are correspondingly plotted in the bottom. Both private signal and public signal have the conditional variance equal to long-run variance of y, i.e.  $\sigma_\epsilon = \sigma_\xi = \sigma_y$. The plotted signals are are a pair of particular draw from their respective conditional distribution. }
		\caption{Nowcasting and Forecasting in Noisy Information}
		\label{IllustrateNI}
	\end{figure}

	NI also predicts non-zero disagreement in the presence of private signals. The behavior of disagreement across agents come from the difference in realized private signals. Specifically, it is equal to the following.

@@

	The implications for disagreement are straightforward. First, the disagreement decrease with the forecast horizon for the reason of discounting. Second, the disagreement depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$. Third, similar to SE, the disagreements also increase with the rigidity parameter $P$ in this model.

@@

	Taking stock, both SE and NI predict rigidity in incorporating the arrival of new information. In the former context, the rigidity comes from the simple non-updating of the most realization of the variable. In the latter case, the rigidity comes from a partial reaction to new information due to the nosiness of the signals.  In addition to forecast and disagreements, the rigidity is also reflected in the dynamics of uncertainty.  Uncertainty in SE does not resolve as rapidly as in FIRE because the newly realized shocks do not get updated by some of the agents. While in NI, the drop in uncertainty is dampened because there is additional uncertainty associated with the real-time realization of the variable.

	Figure \ref{ir_pop} illustrates the impulse response of population moments to a hypothetical one-time shock of size one unit at time $t$ according to different theories. Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to one unconditional standard deviation of $y$.  And the $\lambda$ is set to be $0.25$, implying on average an update interval of four quarters.

	Both FE and disagreements from SE and NI exhibit sluggish adjustment following the shock as we have anticipated. Both pick up in the time of the shock and gradually declines over the horizon as the forecaster approaches terminate date $t+10$. The difference is that in NI, both the forecast and forecast errors move up and downs around the smooth version of the SE since signals are not perfect.

	The dynamic of disagreements and uncertainty, however,  illustrate one parametric difference between SE and NI. In particular,  the initial increase in disagreements is higher for NI compared to SE for the particular parameter values. This implies that the noise of the private signal that drives the disagreements in NI exceeds that the extent to which the agents do not simultaneously update in SE. \footnote{Another subtle point is that if the disagreements jump the highest in the time of the shock turns out depend on value of $\lambda$. In the fixed horizon forecasting, $\lambda=0.5$ is the maximizer of disagreements.}

	For the same parameters, however, the inefficiency seen in dynamics of uncertainty seems to be much more substantial for SE than in NI. Overall, the uncertainty drops almost as efficiently as in FIRE. The difference between SE and the FIRE benchmark is more notable. This is the graphical illustration of Equation \ref{VarSERv}.
